AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
polished introduction

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
In terms of a child-centered AIR, ...
Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for AIR4Children which is presented in section 3. 
Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

>>>>

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade with special focus in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such progress also brings other challenges such as the little to none focus on a centred AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
With regard to child-centered AIR, there is few materials and resources with poor accessble and not appropriately affortable.  
In terms of affortability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
Therefore, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, as a way to minimise cost for hardware and software, section 2 review open source project as the basis of the material for AIR4Children.
In section 3, it is presented three stages of AIR4Children including open source materials and teaching materials based on Montessori education. 
We then conclude this work with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
